---
title: "Supplementary Materials Non-Clinical"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# S0 and S1 Study EDE-Q Restraint Slopes      
This table shows the results of 6 Linear Regressions (nbClicks~AGE+BMI+EDE_Q_Restraint), one per condition for Study 0, Study 1 and the merge of Study 0 + Study 1. \* means *p<0.05*, \*\* means *p<0.01* and \*\*\* means *p<0.001*. BODE stands for *Body Deflate* and BOIN for *Body Inflate*.      

```{r printMLM_S0b, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(multiLevelTable_S0, "pandoc", align = 'r')
```
       
In all cases (Study 0, Study 1 and Study 0 + Study 1) the slope of the *Body Inflate* is more negative than the slope of *Body Deflate*. This means that, in line with our hypothesis, as EDEQ Restraint increases, participants take less risk in *Body Inflate* relative to *Body Deflate*. The results are not statistically significant, but the effect size of the comparison is proportionally high comparing to the slopes (e.g. for Study 0 + Study 1 we have (BODE-BOIN)/BOIN= `r round(100*(printS0S1BODE-printS0S1BOIN)/printS0S1BOIN,1)` %), which indicated that with higher power and a within-participants design, we would be able to measure the relevant interactions more accurately.
      
   


# Main Results Multi-level Step-wise Analysis       

## Clicks ~ Stimulus\*Direction\*EDE-Q Restraint (S0+S1+S2)          
### Models Description     

#### Random Effects     
PARTICIPANT ID (SUBJ_ID), ORDER (OrderF), EXPERIMENTER       

#### Fixed Effects     
```{r avModels_S0S1S2_clicks, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(avModels_S0S1S2_clicks, "pandoc", align = 'r')
```
 
### Step-wise Comparison Results             
     
```{r avRes_S0S1S2_clicks, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(avRes_S0S1S2_clicks, "pandoc", align = 'r')
```
  
### Final Model Coefficients    

```{r sum_S0S1S2_clicks, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(sum_S0S1S2_clicks, "pandoc", align = 'r')
```
        
  
### Inter-correlation Coefficients (final model)    


```{r icc_S0S1S2_clicks, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(icc_S0S1S2_clicks, "pandoc", align = 'r')
```
        
## Hesitance ~ Stimulus\*Direction\*EDE-Q Restraint (S0+S1+S2)       

### Models Description     

#### Random Effects     
Same as for "Clicks".     


#### Fixed Effects     
Same as for "Clicks".     
          
### Step-wise Comparison Results             
     
```{r avRes_S0S1S2_hesitance, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(avRes_S0S1S2_hesitance, "pandoc", align = 'r')
```
  
### Final Model Coefficients    

```{r sum_S0S1S2_hesitance, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(sum_S0S1S2_hesitance, "pandoc", align = 'r')
```
        
  
### Inter-correlation Coefficients (final model)    


```{r icc_S0S1S2_hesitance, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(icc_S0S1S2_hesitance, "pandoc", align = 'r')
```
        


## Probability of Loss (exploration & exploitation) ~ Stimulus\*Direction\*EDE-Q Restraint (S0+S1+S2) 

```{r resultsPBurst, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(resultsPBurst, "pandoc", align = 'r')
```
  
# Model Validation
## Model Validation Exploration vs Exploitation: Coefficient of Variation      
The Coefficient of Variation is higher (significant result) in Exploration than in Exploitation.    

```{r sum_zz2_diff_e, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(round(sum_z1z2_diff_e$coefficients,3), "pandoc", align = 'r')
```


## Model Validation Exploration vs Exploitation:  Prior vs Posterior Hesitance     
Hesitance is higher (significant result) in Exploration than in Exploitation.    

```{r sum_hes1hes2_diff_e_, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(round(sum_hes1hes2_diff_e$coefficients,3), "pandoc", align = 'r')
```



# Control Variable Analysis     
## Correlations: EDE-Q vs Control Variables    
```{r corMatrix_all, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(corMatrix_r, "pandoc", align = 'r')
```


## DASS-21, BIS-11, OCIR, BIDQ covariates for Risk-taking     
To examine the possible effect of covariates in our Risk-taking main findings, we used the same step-wise Multi-level Modelling analysis with final-step models:   
nbClicks~XXX+AGE+BMI+EDE_Q_Restraint+(1|SUBJ_ID)+(1|Order)+(1|Experimenter)     
nbClicks~XXX+AGE+BMI+Stimulus\*Direction\*EDE_Q_Restraint+(1|SUBJ_ID)+(1|Order)+(1|Experimenter)     
where XXX was the relevant Covariate.            

```{r covariatesPumping, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(covariatesPumping, "pandoc", align = 'r')
```
       
We notice that in all cases, the three-way interaction remains statistically significant.    


## DASS-21, BIS-11, OCIR, BIDQ covariates for Hesitance   
To examine the possible effect of covariates in our main Hesitance findings, we used the same step-wise Multi-level Modelling analysis with final-step models:    
hesitance~XXX+AGE+BMI+EDE_Q_Restraint+(1|SUBJ_ID)+(1|Order)+(1|Experimenter)     
hesitance~XXX+AGE+BMI+Stimulus\*Direction\*EDE_Q_Restraint+(1|SUBJ_ID)+(1|Order)+(1|Experimenter)     
where XXX was the relevant Covariate.      
```{r covariatesHesitance, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(covariatesHesitance, "pandoc", align = 'r')
```

We notice that in all cases, the three-way interaction remains statistically significant.        
           
# EDE-Q       

## Correlations: EDE-Q subscales     

```{r corMatrix_edeq, eval=TRUE, echo=FALSE, comment=""}
knitr::kable(corMatrix_r2, "pandoc", align = 'r')
```

## EDE-Q Cronbach Alpha    
S0:   `r cron_alpha_edeq_s0`    
      
S1:   `r cron_alpha_edeq_s1`    

S2:  `r cron_alpha_edeq_s2`    

S0+S1+S2:  `r cron_alpha_edeq_all`    
